---
title: "Manager Incentives"
output: html_document
---


## Setup and Create Functions

###Setup
```{r setup,message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

suppressPackageStartupMessages({

library(tidyverse)
library(reshape2)
library(lubridate)
library(xts)
library(scales)
library(ReporteRs)
library(RollingWindow)
library(parallel)
library(pbapply)
library(dtplyr)
library(matrixStats)
library(data.table)
library(profvis)
library(ggplot2)
library(scales)
library(knitr)

})

#Read in data
returns <- read_csv("//sigisdev/Risk Share/Share/RV/Projects/overdiversification/returns.csv")

#Melt data and select only managers benchmarked to S&P500 and then repivot
returns_melt = melt(returns,id.vars = c("Firm Name","Product Name","Vehicle Name","Benchmark","VT","RM"))


returns_pivot = returns_melt %>% dcast(variable ~ `Firm Name` + `Product Name` + `Vehicle Name`, value.var = "value") %>% as_tibble()

#Change no return months to NA for easier maniupulation
returns_pivot[returns_pivot =="---"] = NA

#Turn date column into date object
returns_pivot$variable = mdy( returns_pivot$variable)


#Only pick managers with full history between 2006/6/30 and 2016/06/30
returns_subset = returns_pivot %>% filter(variable > ymd("2006/06/30"))

#returns_subset = returns_pivot
#returns_subset = returns_subset[colSums(is.na(returns_subset))<nrow(returns_subset)]
returns_subset = returns_subset[colSums(is.na(returns_subset))<1]

returns_subset[,-1] = lapply(returns_subset[,-1],function(x) as.numeric(x)/100)

returns_subset_no_na = returns_subset
returns_subset_no_na[is.na(returns_subset)] = 0
rolling_alpha = RollingSum(returns_subset_no_na[,-1],window = 12,na_method = "ignore" ) %>% as.data.frame()

returns_subset_no_dates = returns_subset[,-1] %>% as.data.frame()
rolling_alpha_df = rolling_alpha %>% as.data.frame()
dates = returns_subset$variable %>% as.data.frame()

managers = 1:ncol(rolling_alpha)

x = 11
returns = returns_subset_no_dates[,x]
alpha = rolling_alpha_df[,x]
allReturns = returns_subset_no_na




```

###Function with buffer

#### Mean TE
```{r function_buffer}

get10Date_months = function(returns,alpha,dates,m,buffer,EOY = FALSE){
        
        
        
        #If buffer is true
        if(buffer) {b = 12} else {b = 0}
        
        
        returns = returns %>% as.data.frame()
        alpha = alpha %>% as.data.frame()
        dates = dates %>% as.data.frame()
        
        #mgr = colnames(alpha)
        
        colnames(alpha) = "returns"
        colnames(returns) = "returns"
        colnames(dates) = "dates"
        
        
        data_alpha = cbind(alpha,dates) %>% as.data.frame() %>%
                arrange(dates) %>%
                mutate(dates = as_date(dates))
        
        dates_alpha = data_alpha %>%
                dplyr::filter(returns>0.1 )#& month(dates)==12)
        
        
        if(EOY){
              dates_alpha = dates_alpha %>% dplyr::filter(month(dates)==12)
        }
        
        
        
        
        if (nrow(dates_alpha) ==0) { 
                
                te_dif = data.frame(0,as_date(0),0,0)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
        } else{
                
                data_returns = cbind(returns,dates) %>% as.data.frame() %>%
                        arrange(dates) %>%
                        mutate(dates = as_date(dates)) 
                
                te_before = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter(dates<= (x %m-% months(b)) & (x %m-% months(m+b)) <= (dates ))
                        stdev = sd(rets_sd$returns,na.rm = T)
                        return(stdev)
                }) %>% as.data.frame()
                
                te_after = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter( dates > x & (dates <= ( x  %m+% months(m))))
                        
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        return(stdev)
                }) %>% as.data.frame()
                
                te_dif = data.frame(dates_alpha,te_before, te_after)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                #colnames(te_dif) = c("before","after")
                #te_dif$dif = te_dif[,1] - te_dif[,2]
                
                
        }
        return(te_dif)
}



```

#### Percentile
```{r function_buffer_perc}

get10Date_months_Perc = function(returns,alpha,dates,m,buffer = FALSE,allReturns,EOY = FALSE){
        
      allReturns = as.data.table(allReturns)  
      
        #If buffer is true
        if(buffer) {b = 12} else {b = 0}
        
        
        returns = returns %>% as.data.frame()
        alpha = alpha %>% as.data.frame()
        dates = dates %>% as.data.frame()
        
        #mgr = colnames(alpha)
        
        
        colnames(alpha) = "returns"
        colnames(returns) = "returns"
        colnames(dates) = "dates"
        
        
        
        data_alpha = cbind(alpha,dates) %>% as.data.table() %>%
                arrange(dates) %>%
                mutate(dates = as_date(dates))
        
        
        dates_alpha = data_alpha %>%
                dplyr::filter(returns>0.1 & dates >= min(dates) %m+% months(m)) #& month(dates)==12)
        
        
        if(EOY){
              dates_alpha = dates_alpha %>% dplyr::filter(month(dates)==12)
        }
        
        
        
        
        if (nrow(dates_alpha) ==0) { 
                
                te_dif = data.frame(0,as_date(0),0,0)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
        } else{
                
                data_returns = cbind(returns,dates) %>% as.data.frame() %>%
                        arrange(dates) %>%
                        mutate(dates = as_date(dates))  %>%
                      as.data.table()
                
                
                
       
                te_before = sapply(dates_alpha$dates,function(x) {
                        
                      
                        date_min = x %m-% months(m+b)
                        date_max = x  %m+% months(m)
                      
                    
                        allReturns_sub = allReturns %>%  dplyr::filter(variable >= date_min & variable < x)
                    
                       
                    
                       #allTE = allReturns_sub %>% select(-variable) %>% summarise_all(sd) %>% t()
                    
                      
                    
                      #allTE = apply(allReturns_sub %>% select(-variable),2,sd)
                      allTE = colSds(allReturns_sub %>% select(-variable) %>% as.matrix())
                    
                        rets_sd =  data_returns %>% dplyr::filter(dates< (x %m-% months(b)) & (x %m-% months(m+b)) <= (dates ))
                    
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        #Takes too long
                        #perc_fun = ecdf(allTE)
                        #perc = perc_fun(stdev)
                        
                        r = rank(c(stdev,allTE))
                        
                        perc = r[[1]]/length(allTE)
                        
                        return(perc)
                }) %>% as.data.frame()
                
                te_after = sapply(dates_alpha$dates,function(x) {
                        print(x)
                        date_min = x %m-% months(m+b)
                        date_max = x  %m+% months(m)
                        
                        allReturns_sub = allReturns %>% dplyr::filter(variable > x & variable <= date_max)
                        
                        if (nrow(allReturns_sub)>0) {
                        
                        #allTE = allReturns_sub %>% select(-variable) %>% summarise_all(sd) %>% t()
                        
                        #allTE = apply(allReturns_sub %>% select(-variable),2,sd)
                        allTE = colSds(allReturns_sub %>% select(-variable) %>% as.matrix())
                        
                        rets_sd =  data_returns %>% dplyr::filter( dates > x & (dates <= ( x  %m+% months(m))))
                        
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        #Takes too long
                        #perc_fun = ecdf(allTE)
                        #perc = perc_fun(stdev)
                        
                        r = rank(c(stdev,allTE))
                        perc = r[[1]]/length(allTE)
                        } else {perc = NA}
                        
                        
                        return(perc)
                }) %>% as.data.frame()
                
                te_dif = data.frame(dates_alpha,te_before, te_after)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                #colnames(te_dif) = c("before","after")
                #te_dif$dif = te_dif[,1] - te_dif[,2]
                
                
        }
        return(te_dif)
}



```

###Function with no overlapping periods

```{r function_overlap}

get10Date_months_no_overlap = function(returns,alpha,dates,m,buffer){
        
        
        #If buffer is true
        if(buffer) {b = 12} else {b = 0}
        
        
        returns = returns %>% as.data.frame()
        alpha = alpha %>% as.data.frame()
        dates = dates %>% as.data.frame()
        
        
        colnames(alpha) = "returns"
        colnames(returns) = "returns"
        colnames(dates) = "dates"
        
        
        data_alpha = cbind(alpha,dates) %>% as.data.frame() %>%
                arrange(dates) %>%
                mutate(dates = as_date(dates))
        
        dates_alpha = data_alpha %>%
                dplyr::filter(returns>0.1 )#& month(dates)==12)
        
        
        
        
        
        
        
        if (nrow(dates_alpha) ==0) { 
                
                te_dif = data.frame(0,as_date(0),0,0)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
        } else{
                
                #Remove Overlapping Periods
                for (i in 1:nrow(dates_alpha)) {
                        
                        d = dates_alpha$dates[i]
                        
                        if(is.na(d)){} else{
                                
                                
                                dates_alpha =  dates_alpha %>%
                                        filter(!(dates >d & dates < d %m+% months(12)))
                        }
                        
                }
                
                #Create Return df
                data_returns = cbind(returns,dates) %>% as.data.frame() %>%
                        arrange(dates) %>%
                        mutate(dates = as_date(dates)) 
                
                
                #Calculate TE before and after
                
                te_before = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter(dates<= (x %m-% months(b)) & (x %m-% months(m+b)) <= (dates ))
                        stdev = sd(rets_sd$returns,na.rm = T)
                        return(stdev)
                }) %>% as.data.frame()
                
                te_after = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter( dates > x & (dates <= ( x  %m+% months(m))))
                        
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        return(stdev)
                }) %>% as.data.frame()
                
                #Calculate Average TE for the rolling period #TODO
                
                
                
                
                #Create Data Frame
                te_dif = data.frame(dates_alpha,te_before, te_after)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
                
        }
        return(te_dif)
}




```

###Vectorize Functions for Number of Months
```{r}

get_Mean_TE_Results = function(cl,months,buffer,rolling_alpha,dates,returns_subset_no_dates){
      
      #Get number of managers
      managers = 1:ncol(rolling_alpha)


      results_months = parLapply(cl,managers, function(x){
              
              print(x)
              
              get10Date_months(
                      returns_subset_no_dates[,x],
                      rolling_alpha[,x],
                      dates,
                      months,
                      buffer
              )})
      
            
      #Name values
      names(results_months) = colnames(returns_subset_no_dates)
      
      #Bind into a dataframe
      results_months_df = bind_rows(results_months,.id = "manager")
      results_months_df$dif = results_months_df$te_before - results_months_df$te_after
      
      te_after_mean =  mean(results_months_df$te_after,na.rm = T)
      te_before_mean =  mean(results_months_df$te_before,na.rm = T)
      
      t_test_result = t.test(results_months_df$te_before,results_months_df$te_after,alternative = "greater",paired = T)
      
      
      te_table =  tribble(
            ~Months, ~Before_TE, ~After_TE, ~Mean_Difference, ~Mean_Difference_Percentage, ~T_Statistic,
            months, te_before_mean, te_after_mean, te_after_mean-te_before_mean, (te_after_mean / te_before_mean) -1, t_test_result$statistic
      )
            
                  
      return(te_table)            
            
      
}

get_Percentile_TE_Results = function(cl,months,buffer,rolling_alpha,dates,returns_subset_no_dates,returns_subset_no_na){
      
      #Get number of managers
      managers = 1:ncol(rolling_alpha)


      results_months_perc = parLapply(cl,managers, function(x){
              
              print(x)
              
              get10Date_months_Perc(
                      returns_subset_no_dates[,x],
                      rolling_alpha[,x],
                      dates,
                      months,
                      buffer,
                      returns_subset_no_na,
                      EOY = FALSE
              )})
      
            
      #Name values
      names(results_months_perc) = colnames(returns_subset_no_dates)

      #Bind into a dataframe???
      results_months_perc_df = bind_rows(results_months_perc,.id = "manager")
      results_months_perc_df$dif = results_months_perc_df$te_before - results_months_perc_df$te_after
      
      te_after_perc =  mean(results_months_perc_df$te_after,na.rm = T)
      te_before_perc =  mean(results_months_perc_df$te_before,na.rm = T)
      
      t_test_result = t.test(results_months_perc_df$te_before,results_months_perc_df$te_after,alternative = "greater",paired = T)

      
      
      te_table =  tribble(
            ~Months, ~Before_TE, ~After_TE, ~Mean_Difference, ~T_Statistic,
            months, te_before_perc, te_after_perc, te_after_perc-te_before_perc, t_test_result$statistic
      )
            
                  
      return(te_table)            
            
      
}


```


###Create Parallel Cluster and Export Functions
```{r parallel_cluster,message=FALSE, warning=FALSE, results='hide',include=TRUE }

suppressPackageStartupMessages({
#Create Parallel Cluster
cl = makeCluster(getOption("cl.cores",4))



#Export needed variables and cuntions
clusterExport(cl,varlist = c("get10Date_months","get10Date_months_Perc",'returns_subset_no_dates','rolling_alpha','dates','returns_subset_no_na'))

clusterEvalQ(cl,library(tidyverse,quietly = T))
clusterEvalQ(cl,library(lubridate,quietly = T))
clusterEvalQ(cl,library(data.table,quietly = T))
clusterEvalQ(cl,library(matrixStats,quietly = T))
})
# 
# 
# results_months = pblapply(cl = cl,X = managers, FUN = function(x){
# 
#         print(x)
# 
#         get10Date_months(
#                 returns_subset_no_dates[,x],
#                 rolling_alpha[,x],
#                 dates,
#                 24,
#                 FALSE
#         )})


```


##Results


###Run Mean TE Function for 6, 12, 24 Month Periods
```{r cache=TRUE}


mean_te_list = lapply(c(6,12,24), function(months){
      
      get_Mean_TE_Results(cl = cl,months = months,buffer = FALSE, rolling_alpha = rolling_alpha, dates = dates, returns_subset_no_dates = returns_subset_no_dates)
      
      
})


mean_te_df = mean_te_list %>% bind_rows() %>%
      mutate_at(c("Before_TE","After_TE","Mean_Difference","Mean_Difference_Percentage"),function(x){percent(round(x,4))}) %>%
      mutate(T_Statistic = round(T_Statistic,2))

kable(mean_te_df)


```

### Mean TE over Time
```{r}

rolling_alpha_df_abs = abs(rolling_alpha_df)

abs_alpha = rowMeans(rolling_alpha_df_abs,na.rm = T) %>% as.data.frame()

abs_alpha$dates = dates[,1]

colnames(abs_alpha) = c("Mean_Absolute_Alpha","Date")


ggplot(abs_alpha,aes(x = Date, y = Mean_Absolute_Alpha)) + geom_line() +
      ggtitle("Trend of Absolute Alpha") + scale_y_continuous(labels = percent) +
      ylab("Mean Absolute Alpha")



```

###Run Mean TE Percentile Function for 6, 12, 24 Month Periods
```{r cache = T}


perc_te_list = lapply(c(6,12,24), function(months){
      
      get_Percentile_TE_Results(
            cl = cl,
            months = months,
            buffer = FALSE,
            rolling_alpha = rolling_alpha,
            dates = dates,
            returns_subset_no_dates = returns_subset_no_dates,
            returns_subset_no_na = returns_subset_no_na)
      
      
})


perc_te_df = perc_te_list %>% bind_rows() %>%
      mutate_at(c("Before_TE","After_TE","Mean_Difference"),function(x){percent(round(x,4))}) %>%
      mutate(T_Statistic = round(T_Statistic,2))

kable(perc_te_df)


```

###Run Mean TE Function With Buffer for 6, 12, 24 Month Periods
```{r cache = TRUE}


mean_te_list_buffer = lapply(c(6,12,24), function(months){
      
      get_Mean_TE_Results(cl = cl,months = months,buffer = TRUE, rolling_alpha = rolling_alpha, dates = dates, returns_subset_no_dates = returns_subset_no_dates)
      
      
})


mean_te_df_buffer = mean_te_list_buffer %>% bind_rows() %>%
      mutate_at(c("Before_TE","After_TE","Mean_Difference","Mean_Difference_Percentage"),function(x){percent(round(x,4))}) %>%
      mutate(T_Statistic = round(T_Statistic,2))

kable(mean_te_df_buffer)


```


###Momentum in Manager Returns

```{r}

monthly_ranks = apply(rolling_alpha %>% na.omit(),1,rank)
monthly_perc = monthly_ranks/nrow(monthly_ranks)

#rolling_alpha_melt = rolling_alpha %>% mutate(n = as.integer(rownames(rolling_alpha))) %>% melt(id.vars = "n")

returns_subset_melt = returns_subset %>% select(-variable) %>% mutate(n = as.integer(rownames(returns_subset))) %>%
        melt(id.vars = "n")

top_decile = monthly_perc %>% melt() %>% filter(value>0.9) %>%
        left_join(returns_subset_melt, by = c("Var2" = "n","Var1" = "variable")) %>%
        group_by(Var2) %>% summarise(ret= mean(value.y))

top_decile_sd = sd(top_decile$ret)


deciles = ( seq(0.0,0.9,0.1))


getDecileSD = function(dec){
        
        decile_ret = monthly_perc %>% melt() %>% filter(value>dec & value < (dec+0.1)) %>%
                mutate(np1 = Var2+1) %>%
        left_join(returns_subset_melt, by = c("np1" = "n","Var1" = "variable")) %>%
        group_by(Var2) %>% summarise(ret= mean(value.y,na.rm = T))

decile_sd = mean(decile_ret$ret,na.rm = T)

return(decile_sd)
        
        }

        


decile_sd_list = sapply(deciles,function(x) getDecileSD(x)) %>% as.data.frame() %>%
        mutate(decile = (deciles+0.1)*10)
colnames(decile_sd_list) = c("TE","Decile")

decile_sd_list = decile_sd_list %>%
      arrange(Decile) %>%
      mutate(Decile = factor (Decile,levels = Decile))

ggplot(decile_sd_list,aes(x = Decile,y= (1+TE)^12 -1)) + geom_col() +
        ylab("Annualized Alpha Over Following Year") +
      scale_x_discrete() +
      scale_y_continuous(label = percent) +
      ggtitle("Momentum in Manager Returns (Sorted by past 12 Month Alpha)")



```