---
title: "Behavior of Mutual Funds"
output: html_notebook
---

## Setup and Create Functions

###Setup
```{r setup}

library(tidyverse)
library(reshape2)
library(lubridate)
library(xts)
library(scales)
library(ReporteRs)
library(RollingWindow)
library(parallel)
library(pbapply)
library(dtplyr)
library(matrixStats)
library(data.table)
library(profvis)
library(ggplot2)
library(scales)

#Read in data
returns <- read_csv("//sigisdev/Risk Share/Share/RV/Projects/overdiversification/returns.csv")

#Melt data and select only managers benchmarked to S&P500 and then repivot
returns_melt = melt(returns,id.vars = c("Firm Name","Product Name","Vehicle Name","Benchmark","VT","RM"))


returns_pivot = returns_melt %>% dcast(variable ~ `Firm Name` + `Product Name` + `Vehicle Name`, value.var = "value") %>% as_tibble()

#Change no return months to NA for easier maniupulation
returns_pivot[returns_pivot =="---"] = NA

#Turn date column into date object
returns_pivot$variable = mdy( returns_pivot$variable)


#Only pick managers with full history between 2006/6/30 and 2016/06/30
returns_subset = returns_pivot %>% filter(variable > ymd("2006/06/30"))

#returns_subset = returns_pivot
#returns_subset = returns_subset[colSums(is.na(returns_subset))<nrow(returns_subset)]
returns_subset = returns_subset[colSums(is.na(returns_subset))<1]

returns_subset[,-1] = lapply(returns_subset[,-1],function(x) as.numeric(x)/100)

returns_subset_no_na = returns_subset
returns_subset_no_na[is.na(returns_subset)] = 0
rolling_alpha = RollingSum(returns_subset_no_na[,-1],window = 12,na_method = "ignore" ) %>% as.data.frame()

returns_subset_no_dates = returns_subset[,-1] %>% as.data.frame()
rolling_alpha_df = rolling_alpha %>% as.data.frame()
dates = returns_subset$variable %>% as.data.frame()

managers = 1:ncol(rolling_alpha)

x = 11
returns = returns_subset_no_dates[,x]
alpha = rolling_alpha_df[,x]
allReturns = returns_subset_no_na




```

###Function with buffer

#### Mean TE
```{r function_buffer}

get10Date_months = function(returns,alpha,dates,m,buffer,EOY = FALSE){
        
        
        
        #If buffer is true
        if(buffer) {b = 12} else {b = 0}
        
        
        returns = returns %>% as.data.frame()
        alpha = alpha %>% as.data.frame()
        dates = dates %>% as.data.frame()
        
        #mgr = colnames(alpha)
        
        colnames(alpha) = "returns"
        colnames(returns) = "returns"
        colnames(dates) = "dates"
        
        
        data_alpha = cbind(alpha,dates) %>% as.data.frame() %>%
                arrange(dates) %>%
                mutate(dates = as_date(dates))
        
        dates_alpha = data_alpha %>%
                dplyr::filter(returns>0.1 )#& month(dates)==12)
        
        
        if(EOY){
              dates_alpha = dates_alpha %>% dplyr::filter(month(dates)==12)
        }
        
        
        
        
        if (nrow(dates_alpha) ==0) { 
                
                te_dif = data.frame(0,as_date(0),0,0)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
        } else{
                
                data_returns = cbind(returns,dates) %>% as.data.frame() %>%
                        arrange(dates) %>%
                        mutate(dates = as_date(dates)) 
                
                te_before = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter(dates<= (x %m-% months(b)) & (x %m-% months(m+b)) <= (dates ))
                        stdev = sd(rets_sd$returns,na.rm = T)
                        return(stdev)
                }) %>% as.data.frame()
                
                te_after = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter( dates > x & (dates <= ( x  %m+% months(m))))
                        
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        return(stdev)
                }) %>% as.data.frame()
                
                te_dif = data.frame(dates_alpha,te_before, te_after)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                #colnames(te_dif) = c("before","after")
                #te_dif$dif = te_dif[,1] - te_dif[,2]
                
                
        }
        return(te_dif)
}



```

#### Percentile
```{r function_buffer_perc}

get10Date_months_Perc = function(returns,alpha,dates,m,buffer = FALSE,allReturns,EOY = FALSE){
        
      allReturns = as.data.table(allReturns)  
      
        #If buffer is true
        if(buffer) {b = 12} else {b = 0}
        
        
        returns = returns %>% as.data.frame()
        alpha = alpha %>% as.data.frame()
        dates = dates %>% as.data.frame()
        
        #mgr = colnames(alpha)
        
        
        colnames(alpha) = "returns"
        colnames(returns) = "returns"
        colnames(dates) = "dates"
        
        
        
        data_alpha = cbind(alpha,dates) %>% as.data.table() %>%
                arrange(dates) %>%
                mutate(dates = as_date(dates))
        
        
        dates_alpha = data_alpha %>%
                dplyr::filter(returns>0.1 & dates >= min(dates) %m+% months(m)) #& month(dates)==12)
        
        
        if(EOY){
              dates_alpha = dates_alpha %>% dplyr::filter(month(dates)==12)
        }
        
        
        
        
        if (nrow(dates_alpha) ==0) { 
                
                te_dif = data.frame(0,as_date(0),0,0)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
        } else{
                
                data_returns = cbind(returns,dates) %>% as.data.frame() %>%
                        arrange(dates) %>%
                        mutate(dates = as_date(dates))  %>%
                      as.data.table()
                
                
                
       
                te_before = sapply(dates_alpha$dates,function(x) {
                        
                      
                        date_min = x %m-% months(m+b)
                        date_max = x  %m+% months(m)
                      
                    
                        allReturns_sub = allReturns %>%  dplyr::filter(variable >= date_min & variable < x)
                    
                       
                    
                       #allTE = allReturns_sub %>% select(-variable) %>% summarise_all(sd) %>% t()
                    
                      
                    
                      #allTE = apply(allReturns_sub %>% select(-variable),2,sd)
                      allTE = colSds(allReturns_sub %>% select(-variable) %>% as.matrix())
                    
                        rets_sd =  data_returns %>% dplyr::filter(dates< (x %m-% months(b)) & (x %m-% months(m+b)) <= (dates ))
                    
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        #Takes too long
                        #perc_fun = ecdf(allTE)
                        #perc = perc_fun(stdev)
                        
                        r = rank(c(stdev,allTE))
                        
                        perc = r[[1]]/length(allTE)
                        
                        return(perc)
                }) %>% as.data.frame()
                
                te_after = sapply(dates_alpha$dates,function(x) {
                        print(x)
                        date_min = x %m-% months(m+b)
                        date_max = x  %m+% months(m)
                        
                        allReturns_sub = allReturns %>% dplyr::filter(variable > x & variable <= date_max)
                        
                        if (nrow(allReturns_sub)>0) {
                        
                        #allTE = allReturns_sub %>% select(-variable) %>% summarise_all(sd) %>% t()
                        
                        #allTE = apply(allReturns_sub %>% select(-variable),2,sd)
                        allTE = colSds(allReturns_sub %>% select(-variable) %>% as.matrix())
                        
                        rets_sd =  data_returns %>% dplyr::filter( dates > x & (dates <= ( x  %m+% months(m))))
                        
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        #Takes too long
                        #perc_fun = ecdf(allTE)
                        #perc = perc_fun(stdev)
                        
                        r = rank(c(stdev,allTE))
                        perc = r[[1]]/length(allTE)
                        } else {perc = NA}
                        
                        
                        return(perc)
                }) %>% as.data.frame()
                
                te_dif = data.frame(dates_alpha,te_before, te_after)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                #colnames(te_dif) = c("before","after")
                #te_dif$dif = te_dif[,1] - te_dif[,2]
                
                
        }
        return(te_dif)
}



```

###Function with no overlapping periods

```{r function_overlap}

get10Date_months_no_overlap = function(returns,alpha,dates,m,buffer){
        
        
        #If buffer is true
        if(buffer) {b = 12} else {b = 0}
        
        
        returns = returns %>% as.data.frame()
        alpha = alpha %>% as.data.frame()
        dates = dates %>% as.data.frame()
        
        
        colnames(alpha) = "returns"
        colnames(returns) = "returns"
        colnames(dates) = "dates"
        
        
        data_alpha = cbind(alpha,dates) %>% as.data.frame() %>%
                arrange(dates) %>%
                mutate(dates = as_date(dates))
        
        dates_alpha = data_alpha %>%
                dplyr::filter(returns>0.1 )#& month(dates)==12)
        
        
        
        
        
        
        
        if (nrow(dates_alpha) ==0) { 
                
                te_dif = data.frame(0,as_date(0),0,0)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
        } else{
                
                #Remove Overlapping Periods
                for (i in 1:nrow(dates_alpha)) {
                        
                        d = dates_alpha$dates[i]
                        
                        if(is.na(d)){} else{
                                
                                
                                dates_alpha =  dates_alpha %>%
                                        filter(!(dates >d & dates < d %m+% months(12)))
                        }
                        
                }
                
                #Create Return df
                data_returns = cbind(returns,dates) %>% as.data.frame() %>%
                        arrange(dates) %>%
                        mutate(dates = as_date(dates)) 
                
                
                #Calculate TE before and after
                
                te_before = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter(dates<= (x %m-% months(b)) & (x %m-% months(m+b)) <= (dates ))
                        stdev = sd(rets_sd$returns,na.rm = T)
                        return(stdev)
                }) %>% as.data.frame()
                
                te_after = sapply(dates_alpha$dates,function(x) {
                        rets_sd =  data_returns %>% dplyr::filter( dates > x & (dates <= ( x  %m+% months(m))))
                        
                        stdev = sd(rets_sd$returns,na.rm = T)
                        
                        return(stdev)
                }) %>% as.data.frame()
                
                #Calculate Average TE for the rolling period #TODO
                
                
                
                
                #Create Data Frame
                te_dif = data.frame(dates_alpha,te_before, te_after)
                colnames(te_dif) = c("returns","dates","te_before","te_after")
                
                
                
        }
        return(te_dif)
}




```

###Create Parallel Cluster and Export Functions
```{r parallel_cluster}

#Create Parallel Cluster
cl = makeCluster(getOption("cl.cores",4),outfile = 'log.txt')

#Export needed variables and cuntions
clusterExport(cl,varlist = c("get10Date_months","get10Date_months_Perc",'returns_subset_no_dates','rolling_alpha','dates','returns_subset_no_na'))

clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(lubridate))
clusterEvalQ(cl,library(data.table))
clusterEvalQ(cl,library(matrixStats))

# 
# 
# results_months = pblapply(cl = cl,X = managers, FUN = function(x){
# 
#         print(x)
# 
#         get10Date_months(
#                 returns_subset_no_dates[,x],
#                 rolling_alpha[,x],
#                 dates,
#                 24,
#                 FALSE
#         )})


```


##Results


###Run Mean TE Function With No Buffer
```{r}

#Get number of managers
managers = 1:ncol(rolling_alpha)




results_months = parLapply(cl,managers, function(x){
        
        print(x)
        
        get10Date_months(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                6,
                FALSE
        )})


#Name values
names(results_months) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_df = bind_rows(results_months,.id = "manager")
results_months_df$dif = results_months_df$te_before - results_months_df$te_after

mean(results_months_df$te_after,na.rm = T)
mean(results_months_df$te_before,na.rm = T)

t.test(results_months_df$te_before,results_months_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_df,aes(dif)) + geom_histogram()




```

###Run Mean TE Function With  Buffer
```{r}

#Get number of managers
managers = 1:ncol(rolling_alpha)




results_months_buffer = parLapply(cl,managers, function(x){
        
        print(x)
        
        get10Date_months(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                6,
                TRUE
        )})


#Name values
names(results_months_buffer) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_buffer_df = bind_rows(results_months_buffer,.id = "manager")
results_months_buffer_df$dif = results_months_buffer_df$te_before - results_months_buffer_df$te_after

mean(results_months_buffer_df$te_after,na.rm = T)
mean(results_months_buffer_df$te_before,na.rm = T)

t.test(results_months_buffer_df$te_before,results_months_buffer_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_buffer_df,aes(dif)) + geom_histogram()




```


###Run Mean TE Function With EOY and No Buffer
```{r}

#Get number of managers
managers = 1:ncol(rolling_alpha)




results_months = parLapply(cl,managers, function(x){
        
        print(x)
        
        get10Date_months(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                24,
                FALSE,
                TRUE
        )})


#Name values
names(results_months) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_df = bind_rows(results_months,.id = "manager")
results_months_df$dif = results_months_df$te_before - results_months_df$te_after

mean(results_months_df$te_after,na.rm = T)
mean(results_months_df$te_before,na.rm = T)

t.test(results_months_df$te_before,results_months_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_df,aes(dif)) + geom_histogram()




```

###Run Mean TE Function With EOY and Buffer
```{r}

#Get number of managers
managers = 1:ncol(rolling_alpha)




results_months_buffer = parLapply(cl,managers, function(x){
        
        print(x)
        
        get10Date_months(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                24,
                TRUE,
                TRUE
        )})


#Name values
names(results_months_buffer) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_buffer_df = bind_rows(results_months_buffer,.id = "manager")
results_months_buffer_df$dif = results_months_buffer_df$te_before - results_months_buffer_df$te_after

results_months_buffer_df = results_months_buffer_df %>% filter(dif != 0)

mean(results_months_buffer_df$te_after,na.rm = T)
mean(results_months_buffer_df$te_before,na.rm = T)

t.test(results_months_buffer_df$te_before,results_months_buffer_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_buffer_df,aes(dif)) + geom_histogram()




```




### Run Percentile Function With No Buffer

```{r}

#Get number of managers
#managers = 1:ncol(rolling_alpha)


#profvis({

results_months_perc = pblapply(cl = cl,X=managers,FUN= function(x){
        
        print(x)
        
        get10Date_months_Perc(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                24,
                FALSE,
                returns_subset_no_na
        )})

#})
#Name values
names(results_months_perc) = colnames(returns_subset_no_dates)

#Bind into a dataframe???
results_months_perc_df = bind_rows(results_months_perc,.id = "manager")
results_months_perc_df$dif = results_months_perc_df$te_before - results_months_perc_df$te_after

mean(results_months_perc_df$te_after,na.rm = T)
mean(results_months_perc_df$te_before,na.rm = T)

t.test(results_months_perc_df$te_before,results_months_perc_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_perc_df,aes(dif)) + geom_histogram()


#saveRDS(results_months_perc,"//sigisdev/Risk Share/Share/RV/Projects/Rational_Behavior/Data/perc_24.rds")

```





### Run Percentile Function With Buffer

```{r}

#Get number of managers
#managers = 1:ncol(rolling_alpha)




results_months_perc_buffer = pblapply(cl=cl,X=managers,FUN= function(x){
        
        print(x)
        
        get10Date_months_Perc(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                12,
                TRUE,
                returns_subset_no_na
        )})


#Name values
names(results_months_perc_buffer) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_perc_buffer_df = bind_rows(results_months_perc_buffer,.id = "manager")
results_months_perc_buffer_df$dif = results_months_perc_buffer_df$te_before - results_months_perc_buffer_df$te_after

mean(results_months_perc_buffer_df$te_after,na.rm = T)
mean(results_months_perc_buffer_df$te_before,na.rm = T)

t.test(results_months_perc_buffer_df$te_before,results_months_perc_buffer_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_perc_buffer_df,aes(dif)) + geom_histogram()


#saveRDS(results_months_perc_buffer,"//sigisdev/Risk Share/Share/RV/Projects/Rational_Behavior/Data/perc_buffer_24.rds")

```




### Run Percentile Function With EOY and Buffer

```{r}

#Get number of managers
#managers = 1:ncol(rolling_alpha)




results_months_perc_buffer_eoy = pblapply(cl=cl,X=managers,FUN= function(x){
        
        print(x)
        
        get10Date_months_Perc(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                12,
                TRUE,
                returns_subset_no_na,
                EOY = TRUE
        )})


#Name values
names(results_months_perc_buffer_eoy) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_perc_buffer_eoy_df = bind_rows(results_months_perc_buffer_eoy,.id = "manager")
results_months_perc_buffer_eoy_df$dif = results_months_perc_buffer_eoy_df$te_before - results_months_perc_buffer_eoy_df$te_after

mean(results_months_perc_buffer_eoy_df$te_after,na.rm = T)
mean(results_months_perc_buffer_eoy_df$te_before,na.rm = T)

t.test(results_months_perc_buffer_eoy_df$te_before,results_months_perc_buffer_eoy_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_perc_buffer_eoy_df,aes(dif)) + geom_histogram()


#saveRDS(results_months_perc_buffer,"//sigisdev/Risk Share/Share/RV/Projects/Rational_Behavior/Data/perc_buffer_24.rds")

```


### Run Percentile Function With EOY and No Buffer

```{r}

#Get number of managers
#managers = 1:ncol(rolling_alpha)




results_months_perc_buffer_eoy = pblapply(cl=cl,X=managers,FUN= function(x){
        
        print(x)
        
        get10Date_months_Perc(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                12,
                FALSE,
                returns_subset_no_na,
                EOY = TRUE
        )})


#Name values
names(results_months_perc_buffer_eoy) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_perc_buffer_eoy_df = bind_rows(results_months_perc_buffer_eoy,.id = "manager")
results_months_perc_buffer_eoy_df$dif = results_months_perc_buffer_eoy_df$te_before - results_months_perc_buffer_eoy_df$te_after

mean(results_months_perc_buffer_eoy_df$te_after,na.rm = T)
mean(results_months_perc_buffer_eoy_df$te_before,na.rm = T)

t.test(results_months_perc_buffer_eoy_df$te_before,results_months_perc_buffer_eoy_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_perc_buffer_eoy_df,aes(dif)) + geom_histogram()


#saveRDS(results_months_perc_buffer,"//sigisdev/Risk Share/Share/RV/Projects/Rational_Behavior/Data/perc_buffer_24.rds")

```

### Run Percentile Function With EOY and Buffer

```{r}

#Get number of managers
#managers = 1:ncol(rolling_alpha)




results_months_perc_buffer_eoy = pblapply(cl=cl,X=managers,FUN= function(x){
        
        print(x)
        
        get10Date_months_Perc(
                returns_subset_no_dates[,x],
                rolling_alpha[,x],
                dates,
                12,
                TRUE,
                returns_subset_no_na,
                EOY = TRUE
        )})


#Name values
names(results_months_perc_buffer_eoy) = colnames(returns_subset_no_dates)

#Bind into a dataframe
results_months_perc_buffer_eoy_df = bind_rows(results_months_perc_buffer_eoy,.id = "manager")
results_months_perc_buffer_eoy_df$dif = results_months_perc_buffer_eoy_df$te_before - results_months_perc_buffer_eoy_df$te_after

mean(results_months_perc_buffer_eoy_df$te_after,na.rm = T)
mean(results_months_perc_buffer_eoy_df$te_before,na.rm = T)

t.test(results_months_perc_buffer_eoy_df$te_before,results_months_perc_buffer_eoy_df$te_after,alternative = "greater",paired = T)

ggplot(results_months_perc_buffer_eoy_df,aes(dif)) + geom_histogram()


#saveRDS(results_months_perc_buffer,"//sigisdev/Risk Share/Share/RV/Projects/Rational_Behavior/Data/perc_buffer_24.rds")

```








### Momentum in Manager Returns
```{r}

monthly_ranks = apply(rolling_alpha %>% na.omit(),1,rank)
monthly_perc = monthly_ranks/nrow(monthly_ranks)

#rolling_alpha_melt = rolling_alpha %>% mutate(n = as.integer(rownames(rolling_alpha))) %>% melt(id.vars = "n")

returns_subset_melt = returns_subset %>% select(-variable) %>% mutate(n = as.integer(rownames(returns_subset))) %>%
        melt(id.vars = "n")

top_decile = monthly_perc %>% melt() %>% filter(value>0.9) %>%
        left_join(returns_subset_melt, by = c("Var2" = "n","Var1" = "variable")) %>%
        group_by(Var2) %>% summarise(ret= mean(value.y))

top_decile_sd = sd(top_decile$ret)


deciles = ( seq(0.0,0.9,0.1))


getDecileSD = function(dec){
        
        decile_ret = monthly_perc %>% melt() %>% filter(value>dec & value < (dec+0.1)) %>%
                mutate(np1 = Var2+1) %>%
        left_join(returns_subset_melt, by = c("np1" = "n","Var1" = "variable")) %>%
        group_by(Var2) %>% summarise(ret= mean(value.y,na.rm = T))

decile_sd = mean(decile_ret$ret,na.rm = T)

return(decile_sd)
        
        }

        


decile_sd_list = sapply(deciles,function(x) getDecileSD(x)) %>% as.data.frame() %>%
        mutate(decile = (deciles+0.1)*10)
colnames(decile_sd_list) = c("TE","Decile")

decile_sd_list = decile_sd_list %>%
      arrange(Decile) %>%
      mutate(Decile = factor (Decile,levels = Decile))

ggplot(decile_sd_list,aes(x = Decile,y= (1+TE)^12 -1)) + geom_col() +
        ylab("Annualized Alpha Over Following Year") +
      scale_x_discrete() +
      scale_y_continuous(label = percent) +
      ggtitle("Momentum in Manager Returns (Sorted by past 12 Month Alpha)")



```


### Mean TE over Time
```{r}

rolling_alpha_df_abs = abs(rolling_alpha_df)

abs_alpha = rowMeans(rolling_alpha_df_abs,na.rm = T) %>% as.data.frame()

abs_alpha$dates = dates[,1]

colnames(abs_alpha) = c("Mean_Absolute_Alpha","Date")


ggplot(abs_alpha,aes(x = Date, y = Mean_Absolute_Alpha)) + geom_line() +
      ggtitle("Trend of Absolute Alpha") + scale_y_continuous(labels = percent) +
      ylab("Mean Absolute Alpha")



```

